Hurricane Evacuation Strategies for the State of Mississippi

### 2015-11-16 manuscript.tex
Added missing edge

\section{Heuristic Model of Landfall-Avodiant Evacuations}

@@

    \par This model's main goal is to find the amount of time it takes to evacuate the affected counties, given the estimated floods. After 100 simulations with the parameters described above, we find that it consistently takes less than 50 hours to evacuate all the at-risk counties. Figures \ref{fig:stochastic_out_large} and \ref{fig:stochastic_out_small} depict the evolution of the county populations when the impending hurricane is of category 1 and 5 respectively. The hurricane in Figure~\ref{fig:stochastic_out_large} is coming from the West, and a such, the population of Jackson County initially peaks as everyone moves east and directly away from the hurricane's projected landfall, then decreases as citizens start then making their way north and out of the state. In Figure~\ref{fig:stochastic_out_small}, the hurricane comes directly from the South. There is a slight flaw in the graph in that Harrison County is represented to be lower than Jackson County, and the connectivity between the two is quite high. As such, people from Harrison County will seek refuge in Jackson County before moving North.

@@

@@

\section{Conclusions}
\label{sec:conclusions}

@@

\section{Individual Contributions}
\label{sec:contributions}
\subsection*{Ryan}
Performed the data-fetching of the hurricanes. Wrote all of the most of the manuscript with Paul. Worked out some of the logic for both the flow and the markov model.

\subsection*{Paul}
Designed and implemented the stochastic model. Helped Ryan write most of the manuscript. Parsed the county data such as county location and population using the WolframAlpha API.

>>>>

\section{Heuristic Model of Landfall-Avoiding Evacuations}

@@

    \par This model's main goal is to find the amount of time it takes to evacuate the affected counties, given the estimated floods. After 100 simulations with the parameters described above, we find that it consistently takes less than 50 hours to evacuate all the at-risk counties. Figures \ref{fig:stochastic_out_large} and \ref{fig:stochastic_out_small} depict the evolution of the county populations when the impending hurricane is of category 5 and 1 respectively. The hurricane in Figure~\ref{fig:stochastic_out_large} is coming from the West, and a such, the population of Jackson County initially peaks as everyone moves east and directly away from the hurricane's projected landfall, then decreases as citizens start then making their way north and out of the state. In Figure~\ref{fig:stochastic_out_small}, the hurricane comes directly from the South. There is a slight flaw in the graph in that Harrison County is represented to be lower than Jackson County, and the connectivity between the two is quite high. As such, people from Harrison County will seek refuge in Jackson County before moving North.

@@

      \caption{Evacuation Comparison for Category 5 and 1 Hurricanes}

@@

\section{Conclusions}
\label{sec:conclusions}
\par The first thing that we want to conclude on is that two of our models agree on the fact that there is a large amount of congestion in the Southern area of Mississippi. Congestion in this area is not ideal, and in fact dangerous, since it is the area most likely to be flooded by hurricanes. This congestion seems to be caused by a lack of highway coverage in the Southwestern part of Mississippi, especially between Stone, Perry, Greene and George counties. In fact, adding a Four-Lane Highway between George and Perry Counties moves the bottleneck of traffic flow to a considerably safer area up North. Our strongest recommendation to the State of Mississippi, as  a preventative measure, is to consider such a highway.\\

\par Finally, we can conclude on the strategy to use, depending on the situation. The Heuristic Model is a model where all citizens decide where they are going on their own, and in which county officials do not need to intervene. As such, this model leads to the highest evacuation speeds, at the cost of having a place for the citizens to take refuge. Therefore this strategy should only be used in the most urgent scenario, where everyone absolutely must leave the affected counties as quickly as possible. On the other hand, if the State has had more time to prepare and has forecasted the arrival of the hurricane early enough, then they can tell the citizens to stay in-state, make accommodations for them, and give them very specific routes according to either the Markov Model or the Maxflow Model. This is a more heavy-handed strategy and would invariably involve a lot of intervention from the county officials in order to properly organize the evacuations.

@@

\section{Individual Contributions}
\label{sec:contributions}
\subsection*{Ryan}
Performed the data-fetching of the hurricanes. Wrote all of the most of the manuscript with Paul. Worked out some of the logic for both the flow and the Markov model.

\subsection*{Paul}
Designed and implemented the stochastic model. Helped Ryan write most of the manuscript. Parsed the county data such as county location and population using the WolframAlpha API. Created the Mississippi Highway map used in all the models.
